\documentclass[10pt]{resume}

\usepackage[left=0.45in,top=0.35in,right=0.45in,bottom=0.35in]{geometry}


\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Shubh Agnihotri}
\address{+91 9335451432 \\ Lucknow, Uttar Pradesh, India}
\address{\href{mailto:shubh2004@gmail.com}{shubh2004@gmail.com} \\ 
\href{https://www.linkedin.com/in/lawk0/}{linkedin.com/in/lawk0} \\ 
\href{https://github.com/lawk-0}{github.com/lawk-0}}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{Objective}
Aspiring AI/ML Engineer with a strong foundation in computer science, data structures, and algorithms. Skilled in Python, C++, and Java, with hands-on experience in machine learning, NLP, and automation systems. Passionate about developing intelligent, data-driven solutions.
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{@{}p{2in}p{5in}}
Programming Languages & Python, C++, Java, C, Go, SQL, JavaScript \\[3pt]
Libraries / Frameworks& NumPy, Pandas, Matplotlib, Scikit-learn, TensorFlow, Keras, PyTorch, Seaborn \\[3pt]
AI / ML Concepts & Data Preprocessing, Supervised \& Unsupervised Learning, NLP, Reinforcement Learning \\[3pt]
Tools \& Platforms & VS Code, Oracle Cloud (OCI), Github and Git, Selenium, Flask, PyQt5, Jupyter Notebook\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\item \textbf{AI Assistant Automation System} — Built a Python-based AI system integrating Selenium, Groq API, and PyQt5 for automation and voice interaction.

\item \textbf{AI Resume Screening System} — Designed an NLP classifier using spaCy and Scikit-learn for context-aware hiring predictions.

\item \textbf{Real-Time Search Engine} — Developed a Groq-powered engine with instant, ranked search results via Python web automation.

\item \textbf{AI Sentiment Analysis System} — Implemented sentiment classification using TF-IDF and Logistic Regression models.

\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Certifications}

\item \textbf{\href{https://unstop.com/certificate-preview/aa08da16-c97e-4261-a363-0043d38befc9}{Adobe India Hackathon (2025)}} — Qualified for Round 1 (Online MCQ + Coding Challenge).

\item \textbf{\href{https://catalog-education.oracle.com/pls/certview/sharebadge?id=719FD170B4B05E469E06593E7B1C2D3E97A4E88D0AA2AFFF78C357C5D80D9C3A}{OCI AI Foundations Associate (Oracle, 2025)}} — Hands-on learning in AI, ML, and Generative AI on Oracle Cloud.

\item \textbf{\href{https://www.udemy.com/certificate/UC-27504e9e-2fd1-49ee-a7e5-4f3ab294f2b4}{Machine Learning with Python (Udemy, 2025)}} — Implemented core ML algorithms, NLP, and deep learning in Python.

\item \textbf{\href{https://www.codechef.com}{CodeChef Skill Series (2024–2025)}} — Completed tracks in C, C++, Java, Python, Go, SQL, NumPy, Pandas, and algorithmic problem-solving.

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.Tech in Computer Science and Engineering}, Kalinga Institute of Industrial Technology (KIIT University), Bhubaneswar \hfill {Ongoing, 3rd Year, CGPA: 8.22}\\
{\bf City Montessori School, Gomtinagar-I}, Lucknow \hfill {Intermediate (XII) – 91\%}\\
{\bf St. Francis' College}, Lucknow \hfill {High School (X) – 84.8\%}\\

\end{rSection}

\end{document}
