\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage[hidelinks]{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Shubh Agnihotri}
\address{+91 9335451432 \\ Lucknow, Uttar Pradesh, India}
\address{\href{mailto:shubh2004@gmail.com}{shubh2004@gmail.com} \\ 
\href{https://www.linkedin.com/in/lawk0/}{linkedin.com/in/lawk0} \\ 
\href{https://github.com/lawk-0}{github.com/lawk-0}}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{Objective}
Aspiring AI/ML Engineer with a strong foundation in computer science, data structures, and algorithms. Skilled in Python, C++, and Java, with hands-on experience in machine learning, NLP, and real-time AI systems. Passionate about developing intelligent automation and data-driven applications.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.Tech in Computer Science and Engineering}, Kalinga Institute of Industrial Technology (KIIT University), Bhubaneswar \hfill {Ongoing, 3rd year, CGPA: 8.22 (2nd year end)}\\

{\bf City Montessori School, Gomtinagar-I}, Lucknow \hfill {Intermediate (XII) – 91\%}\\

{\bf St. Francis' College}, Lucknow \hfill {High School (X) – 84.8\%}\\

\end{rSection}


%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l}
\textbf{Programming Languages} & Python, C++, Java, C, Go, SQL, JavaScript\\
\textbf{Libraries/Frameworks} & NumPy, Pandas, Matplotlib, Scikit-learn, TensorFlow, Keras, PyTorch, Seaborn, StatsModels\\
\textbf{Machine Learning Concepts} & Data Preprocessing, Supervised/Unsupervised Learning, Model Evaluation, Regularization, NLP, Reinforcement Learning\\
\textbf{Tools \& Platforms} & Oracle Cloud Infrastructure (OCI), Git, Selenium, PyQt5, Jupyter Notebook\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\item \textbf{AI Assistant Automation System} — Developed a desktop-based AI assistant featuring real-time web search, voice interaction, image generation, and GUI automation using Python, Selenium, and PyQt5. Integrated speech recognition and text-to-speech for conversational flow.

\item \textbf{AI Resume Screening System} — Built an NLP-powered recruitment assistant using spaCy and scikit-learn to classify resumes as 'Hired' or 'Not Hired'. Designed contextual understanding beyond keyword matching and built a dashboard with Flask for visualization.

\item \textbf{Real-Time Search Engine} — Created an intelligent search system leveraging Groq API and web scraping with dynamic ranking. Enabled instant retrieval of factual and up-to-date responses.

\item \textbf{AI Sentiment Analysis System} — Implemented a machine learning pipeline using NLP techniques (TF-IDF, Logistic Regression) to analyze sentiment in user reviews and social media data.

\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Certifications}

\item \textbf{\href{https://catalog-education.oracle.com/pls/certview/sharebadge?id=719FD170B4B05E469E06593E7B1C2D3E97A4E88D0AA2AFFF78C357C5D80D9C3A}{OCI AI Foundations Associate (Oracle, 2025)}} — Hands-on training in AI, ML, Deep Learning, and Generative AI within Oracle Cloud Infrastructure.

\item \textbf{\href{https://www.udemy.com/certificate/UC-27504e9e-2fd1-49ee-a7e5-4f3ab294f2b4}{Machine Learning with Python (Udemy, 2025)}} — Gained practical experience in ML models, reinforcement learning, NLP, and deep learning implementation.

\item \textbf{\href{https://unstop.com/certificate-preview/aa08da16-c97e-4261-a363-0043d38befc9}{Adobe India Hackathon (2025)}} — Qualified for Round 1 (Online MCQ + Coding Challenge).

\item \textbf{\href{https://www.codechef.com/users/shubh1_234/certificates}{CodeChef Skill Series (2024–2025)}} — Courses in C, C++, Java, Python, Go, SQL, NumPy, Pandas, Time Complexity, and Logic Building.

\end{rSection}

%----------------------------------------------------------------------------------------
%	RELEVANT EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Relevant Experience}

\item \textbf{SIH 2025 Internals Hackathon} — Participated in Smart India Hackathon 2025 internal round, contributing to AI/ML-based solutions in a team setting.

\item \textbf{Adobe India Hackathon (2025)} — Qualified Round 1 (Online MCQ + Coding Challenge), applied AI/ML skills to real-world problem statements.

\item \textbf{Amazon ML Challenge (2025)} — Worked on practical ML problems, building and evaluating models for real-world datasets.

\item \textbf{AI Resume Screening System} — Built an NLP-powered recruitment assistant using spaCy and scikit-learn to classify resumes as 'Hired' or 'Not Hired'. Designed contextual understanding and built a dashboard with Flask for visualization.

\item \textbf{AI Assistant Automation System} — Developed a desktop-based AI assistant featuring real-time web search, voice interaction, image generation, and GUI automation using Python, Selenium, and PyQt5.

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR / LEADERSHIP
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular \& Leadership}

\begin{itemize}
    \item Active participant in AI and open-source communities; contributed to automation and ML-based projects.
    \item Continuous learner, pursuing self-driven AI research and certifications to deepen technical proficiency.
    \item Engaged in building AI solutions that integrate NLP, automation, and real-time data analysis.
\end{itemize}

\end{rSection}



\end{document}
